\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
2.3.1 Cov sph: comma + removed extra =

        As described in Section \ref{ssec:theory.pcl}, in the curved-sky estimator it is common to first average over the harmonic number $m$ as part of the bandpower binning operation. Let us therefore define

@@

        The covariance of these objects under the approximation in Eq. \ref{eq:covar_efstathiou}, can be computed as:

@@

          ^{af}_{bg}\mathcal{W}^{\alpha\phi,\alpha'\phi'}_{\beta\gamma,\beta'\gamma'}(\ell,\ell')=\equiv\sum_{m=-\ell}^\ell \sum_{m'=-\ell'}^{\ell'}\frac{\,^{af}W^{\alpha\phi,\alpha'\phi'}_{{\bf l}{\bf l}'}\left(\,^{bg}W^{\beta\gamma,\beta'\gamma'}_{{\bf l}{\bf l}'}\right)^*}{(2\ell+1)(2\ell'+1)}.

>>>>

        As described in Section \ref{ssec:theory.pcl}, in the curved-sky
        estimator it is common to first average over the harmonic number $m$
        as part of the bandpower binning operation. Let us, therefore, define

@@

        The covariance of these objects, under the approximation in Eq. \ref{eq:covar_efstathiou}, can be computed as:

@@

          ^{af}_{bg}\mathcal{W}^{\alpha\phi,\alpha'\phi'}_{\beta\gamma,\beta'\gamma'}(\ell,\ell')\equiv\sum_{m=-\ell}^\ell \sum_{m'=-\ell'}^{\ell'}\frac{\,^{af}W^{\alpha\phi,\alpha'\phi'}_{{\bf l}{\bf l}'}\left(\,^{bg}W^{\beta\gamma,\beta'\gamma'}_{{\bf l}{\bf l}'}\right)^*}{(2\ell+1)(2\ell'+1)}.
